Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-05 workflow/workflow.Rmd
Updated package versions to latest

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
if(packageVersion("zinbwave")<"0.99.5") stop("must have current devel version to avoid bugs")
if(packageVersion("clusterExperiment")<"1.3.1.9003") stop("must have current develop version to avoid bugs")
if(packageVersion("scone")<"1.1.2") stop("must have current devel version to avoid bugs")

@@

if(!file.exists("../data/GSE95601_oeHBCdiff_Cufflinks_eSet.Rda")) {
  download.file(urls[1], "../data/GSE95601_oeHBCdiff_Cufflinks_eSet.Rda.gz")
  gunzip("../data/GSE95601_oeHBCdiff_Cufflinks_eSet.Rda.gz")
}

@@

```{r,echo=FALSE}
par(mfrow = c(1,1))
```

>>>>

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
if(packageVersion("zinbwave")<"0.99.6") stop("must have current devel version to avoid bugs")
if(packageVersion("clusterExperiment")<"1.3.1.9004") stop("must have current develop version to avoid bugs")
if(packageVersion("scone")<"1.1.2") stop("must have current devel version to avoid bugs")

@@

if(!file.exists("../data/GSE95601_oeHBCdiff_Cufflinks_eSet.Rda")) {
  download.file(urls[1], "../data/GSE95601_oeHBCdiff_Cufflinks_eSet.Rda.gz")
  R.utils::gunzip("../data/GSE95601_oeHBCdiff_Cufflinks_eSet.Rda.gz")
}

@@
